---
title: "Challenges - Day 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
books <- read_csv('data/books.csv')
```

## Data Cleaning & Transformation

### Rename `CALL...ITEM.`

1. To rename a variable in `books` we used earlier: 

```{r renaming2}
# rename the . Make sure you return (<-) the output to your 
# variable, otherwise it will just print it to the console
books <- rename(books,
                title = X245.ab)
```

**Fill in the blanks**. Rename the `CALL...ITEM.` column to `callnumber2`. Remember to add the period to the end of the `CALL...ITEM.`

```{r, eval=FALSE}
 books <- ____(books,
                 callnumber2 = _________)
```

### Filtering with `filter()`

Earlier we used the `filter()` function to subset the data for only items coded books. 

```{r, eval=FALSE}
bookCheckouts <- filter(books,
                        format == "book",
                        tot_chkout  0)
```


1. Using `filter()`, create a data frame called `booksJuv` consisting of `format` books and `subCollection` juvenile materials. 

2. Use `mean()` to check the average number of checkouts for the `booksJuv` data frame.

### Your answer (fill in the blanks)
```{r,eval=FALSE}
______ <- filter(books,
                   format == "_____",
                   ________ ==  "_______")
___(booksJuv$tot_chkout)
```


### Playing with pipes `%%`

1. Create a new data frame `booksKids` with these conditions:
* `filter()` to include `subCollection` juvenile & k-12 materials and `format` books. 
* `select()` only title, call number, total checkouts, and publication year
* `arrange()` by total checkouts in descending order
2. Use `mean()` to check the average number of checkouts for the `booksJuv` data frame.

### Solution
```{r, eval=FALSE}
booksKids <- books %%
  filter(subCollection %in% c("juvenile", "k-12 materials"),
  format == "book") %%
  select(title, callnumber, tot_chkout, pubyear) %%
  arrange(desc(tot_chkout))
```


## Data Viz 

### Plotting Exercise

Boxplots are useful summaries, but hide the *shape* of the distribution. For
example, if the distribution is bimodal, we would not see it in a
boxplot. An alternative to the boxplot is the violin plot, where the shape
(of the density of points) is drawn.

**Replace the box plot with a violin plot; see `geom_violin()`.**

### Fill in the blank. 

```{r violin-plot, eval=FALSE}
ggplot(data = booksHighUsage, aes(x = call_class, y = tot_chkout)) +
  geom_____(alpha = 0) +
  geom_jitter(alpha = 0.5, color = "tomato")
```

Now, add color to the `geom_jitter` argument on your boxplot according to the item `subCollection`. *Hint:* If you get the error `object 'subCollection' not found` or `invalid color name 'subCollection'` then consider `color` as an aesthetic mapping.

###  Solution
```{r boxplot-exercise-subcollection, eval=F}
ggplot(data = booksHighUsage, aes(x = call_class, y = tot_chkout)) +
  geom_violin(alpha = 0) +
  geom_jitter(alpha = 0.5, aes(color = subCollection)) +
  scale_y_log10()
```

 So far, we've looked at the distribution of checkouts within call number ranges. Try
 making a new plot to explore the distribution of checkouts within another variable.

 - Still using the `booksHighUsage` data, create a boxplot for `tot_chkout` for each `subCollection`. Overlay the boxplot layer on a jitter layer to show actual measurements. Keep the `scale_y_log10` argument.

### Solution
```{r, eval=FALSE}
  ggplot(data = booksHighUsage, aes(x = subCollection, y = tot_chkout)) +
   geom_boxplot(alpha = 0) +
   geom_jitter(alpha = 0.5, color = "tomato") +
   scale_y_log10()
```


### Challenge

 Use the `books2` data to create a bar plot that depicts the number of items in
each sub-collection, faceted by format.
 Add the scale_y_log10() argument to
create a logarithmic scale for easier visibility.
 Add the following theme
argument to tilt the axis text diagonal: `theme(axis.text.x = element_text(angle
= 60, hjust = 1))`

###  Solution
```{r average-weight-time-series, eval=FALSE}
  ggplot(data = books2, aes(x = subCollection)) +
  geom_bar() +
  facet_wrap(vars(format)) +
  scale_y_log10() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

