---
title: "Library Carpentry R - Part 2"
output: html_document
author: "Tim Dennis"
date: 2021-05-21
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Last week review using RMarkdown

* At the end of the class we used a cleaned up version of the raw `books.csv` that was derived from the University of Houston–Clear Lake Integrated Library System in 2018.
* It is a random sample of books from the catalog. 
* It consists of 10,000 observations of 11 variables. 
* We read in this data from a url like so: 

```{r books2}
books2 <- read_csv("https://raw.githubusercontent.com/LibraryCarpentry/lc-r/main/data/books_reformatted.csv")
```

We looked at the data using `glimpse`. 

```{r glimps-books}
glimpse(books2)
```

We created a subset of the data retaining only books that are in the "general collection", "juvenile" and "k12 materials" sub-collections. 

```{r subset-books-subcol}
books_plot <- books2 %>% 
  filter(subCollection == "general collection" |
         subCollection == "juvenile" |
         subCollection == "k12 materials",
         !is.na(call_class))
```

We then plotted the data using ggplot: 

```{r bar-call-class}
ggplot(data = books_plot, mapping = aes(x = call_class)) + geom_bar()
```

## This week! 

### Schedule 

| Topic | Time |
| ------- | ----- | 
| Introduction to RMarkdown documents & review | 9:10 am -9:20 am |
| Reading in data and inspecting dataframes | 9:20 am - 9:30 am |
| Challenges | 9:45 am - 9:55 am |
| Break | 9:55 - 10:05 | 
| Cleaning and preparing data in R | 10:05 am - 10:45 am | 
| Challenges | 10:45 - 10:55 am |
| Break | 10:55 - 11:05 am |
| Visualizing data in R | 11:05 am - noon |
| Challenges |  | 
| Break noon | 12:10 |  


